---
Levi Makwei"
output: html_document
---

design a " feature selection algorithm", that is, an algorithm which will select several good columns to use in multidimensional linear regression.

The algorithm should work as follows:

- You start with a list `predictors` of all possible independent variables, that is, all columns, except for `price`, `make`, and `X`.

- Initially, you have an empty list `sp` of selected predictors, we will do several rounds, on each adding one of the predictors to this list, and will stop when either all predictors are in `sp`, or termination condition (to be discussed later) is met.

- On each round, go over each predictor `p` not in `sp`, and compute the adjusted $R^2$ for the model with predictors `c(sp, p)`. Select the one producing the maximal $R^2$ - that is your candidate for appending to `sp`.

- If adjusted $R^2$ is higher for `c(sp, p)` than for `sp`, then add `p` to `sp`. Otherwise terminate.

As a result of this algorithm you should obtain an (ordered) list of columns to be used in `lm`. For this exercise it is enough to print this list, although normally after that you would want to actually run the regression with this predictors.

```{r, message=FALSE, warning=FALSE}
library(ggplot2)
library(tidyverse)
auto <- read.csv("auto.csv")


predictors <- colnames(auto) 
predictors <- predictors[!predictors %in% c("X", "make", "price")]
predictors


#Write your code here

dv <- "price"

optimize <- function(predictors, sp){
  dif <- unique(predictors[!predictors %in% sp ])
  if (length(dif) == 0){
    return (sp)
  }
  
 
  maxR1 = 0
  candidate = dif[0]
  
  for (p in dif){

    sm <- summary(lm(reformulate(termlabels = c(sp,p), response= dv), data = auto))
    R1 <- sm$adj.r.squared
    
    if (maxR1 < R1){
      candidate = p
      maxR1 = R1
    } 
    
  }

    R1 = 0
    if (length(sp == 0)){
    sm1 <- summary(lm(reformulate(termlabels = sp, response= dv), data = auto))
    R1 = sm1$adj.r.squared
    }
    sm2 <- summary(lm(reformulate(termlabels = c(sp, candidate), response=dv), data = auto))
    
    R2 = sm2$adj.r.squared
    
    if (R2 > R1){
      sp <- c(sp, candidate)
      return (optimize(predictors, sp))
    } 
    
    return (sp)
    
}

sp <- c()
optimals <- optimize (predictors, sp)


#summary(lm(reformulate(termlabels = optimals, response=dv), data = auto))

#summary(lm(price ~ weight + foreign + length + displacement + turn, data = auto))

optimals

summary(lm(price ~ weight + foreign + length + displacement + turn, data = auto))

#The answer should be:
## [1] "weight"       "foreign"      "length"       "displacement" "headroom"    
## [6] "turn"
```

**Hint** For this HW, you will need to run the `lm` multiple times, using different formulas. Thus, you need a way of constructing the formulas *dynamically*. This can be done by a function `reformulate`. Consider the following example:

```{r}
str(auto)
sp = c("weight", "foreign", "length")
formula = reformulate(termlabels = sp, response='price')
formula
model <- lm(formula, auto) # Same as lm(price ~ weight + foreign + length, auto)
summary(model)
```

